Titeltext

### 2018-07-25 thesis/paper/paper.tex
Added value type

\section{Wikidata constraints explained}
This section will explain all interesting, meaning translatable or partially translatable, currently used property constraints on Wikidata. They will be presented rougly in descending order of the number of properties with this constraint, although constraints with very similar function will be explained directly after one another. Also, all constraints that were considered untranslatable are listed at the and, each with a short explanation as to why they were placed in that group.\\

@@

\subsection{Type (Q21503250)}
The type constraint requires the existence of either one of a specific statement (instanceOf <class>) or a chain of statements using subclassOf to connect directly (subclassOf* <class>)
or via instanceOf (instanceOf/subclassOf* <class>) for all classes.
\begin{table}[H]
\caption{type constraint (Q21503250)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & chain of statements \\
\hline
Qualifiers & \makecell{relation (P2309) -- 1 \\ must be instance of (Q21503252), subclass of (Q21514624), \\ or instance or subclass of (Q30208840); \\ specifies the relation the constrained item must have to the classes\\
class (P308) -- 1..* \\ entities that must be reached using the relation} \\
\hline
Violation & constrained item without relation to a class \\
\hline
Dependency & \makecell{statements of constrained items using instanceOf (P31) or subclassOf(P279) \\ all statements using subclassOf (P279) }\\
\hline
Rule features & inequality, negation \\
\hline
\end{tabularx}
\end{table}

@@

>>>>

\section{Wikidata constraints explained}
This section will explain all interesting, meaning translatable or partially translatable, currently used property constraints on Wikidata. They will be presented rougly in descending order of the number of properties with this constraint, although constraints with similar function will be explained directly after one another. Also, all constraints that were considered untranslatable are listed at the and, each with a short explanation as to why they were placed in that group.\\

@@

\subsection{Type (Q21503250)}\label{subsec_type}
The type constraint requires the existence of either one of a specific statement (instanceOf <class>) or a chain of statements using subclassOf to connect directly (subclassOf* <class>)
or via instanceOf (instanceOf/subclassOf* <class>) for all classes on the constrained item.
\begin{table}[H]
\caption{type constraint (Q21503250)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & chain of statements \\
\hline
Qualifiers & \makecell{relation (P2309) -- 1 \\ must be instance of (Q21503252), subclass of (Q21514624), \\ or instance or subclass of (Q30208840); \\ specifies the relation the constrained item must have to the classes\\
class (P308) -- 1..* \\ entities that must be reached using the relation} \\
\hline
Violation & constrained item without relation to a class \\
\hline
Dependency & \makecell{statements of constrained items using instanceOf (P31) or subclassOf(P279) \\ all statements using subclassOf (P279) }\\
\hline
Rule features & inequality, negation \\
\hline
\end{tabularx}
\end{table}

@@

\subsection{Value type (Q21510865)}
The value type constraint works like the type constraint (see \ref{subsec_type}) except the statement chains are required on the value of the constrained statement instead of the constrained item. It will thus not be expanded upon.
